Bootstrap 0.1

### 2024-07-15 Rmd/boostrap_0.1.Rmd
some progress on bootstrap routine. create basic shell for some functions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(data.table)
library(tidytable)
library(purrr)
```

@@

## Take what I learned from above and make it better
```{r}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(data.table)
library(tidytable)
library(purrr)
library(tictoc)
library(furrr)
```

@@

## rename the booted length list
